\huge {\normalfont High-Contrast Coronagraphy}

### 2025-06-01 src/tex/ms.tex
for arxiv

\newcommand{\project}[1]{\textsf{#1}}
\hypersetup{%
        colorlinks,
        breaklinks=true,
        plainpages=false,%
        citecolor=[rgb]{0,0.20,0.45},
        linkcolor=[rgb]{0,0.20,0.45},
        urlcolor=[rgb]{0,0.20,0.45},
        bookmarksopen=true,%
        bookmarksnumbered=false,%
        bookmarksdepth=5%
}
% Document starts
\begin{document}

% Page header
\markboth{Kenworthy \& Haffert}{HCC}

%TC:ignore

% Title
\title{High Contrast Coronagraphy}

%Authors, affiliations address.
\author{Matthew Kenworthy$^1$ and Sebastiaan Haffert$^{1,2}$
  \affil{$^1$Leiden Observatory, Niels Bohrweg 2, Leiden 2300RA, The Netherlands; email: kenworthy@strw.leidenuniv.nl}
  \affil{$^2$University of Arizona, Steward Observatory, 933 N. Cherry Avenue, Tucson, Arizona, United States; email: haffert@strw.leidenuniv.nl}}

% Abstracts should include 3–5 bullet points citing actual conclusions of the review. Please limit the abstract to no more than 200 words, including the bullet points. If using TeX, use a “\hangindent=.3cm$bullet$” command at the beginning of each bullet-point paragraph. [The “\begin{itemize}” environment may require the use of a “hardwired” line return (i.e., the ”\\” command) within the environment, as lines may not automatically return in the compiled version.]
%Abstract
\begin{abstract}
Imaging terrestrial exoplanets around nearby stars is a formidable technical challenge, requiring the development of coronagraphs to suppress the stellar halo of diffracted light at the location of the planet.
%
In this Review, we derive the science requirement for high contrast imaging, give an overview of diffraction theory and the Lyot coronagraph, and define the parameters used in our optimization.
%
We detail the working principles of coronagraphs both in laboratory and on-sky with current high contrast instruments, and detail the required algorithms and processes necessary for terrestrial planet imaging with the extremely large telescopes and proposed space telescope missions.

\begin{itemize}
    \item Imaging terrestrial planets around nearby stars is possible with \\ 
    a combination of coronagraphs and active wavefront control \\
    using feedback from wavefront sensors.
    \item Ground based 8-40m class telescopes can target the habitable \\ 
    zone around nearby M dwarf stars with contrasts of $10^{-7}$ and \\
    space telescopes can search around solar-type stars with \\
    contrasts of $10^{-10}$.
    \item Focal plane wavefront sensing, hybrid coronagraph designs and \\
    multiple closed loops providing active correction are required \\
    to reach the highest sensitivities.
    \item Polarization effects need to be mitigated for reaching $10^{-10}$ \\ contrasts whilst keeping exoplanet yields as high as possible.
    \item Recent technology development, including photonics and MKIDs, \\
    will be folded into high contrast instruments.
\end{itemize}

@@

%Keywords, etc.
\begin{keywords}
 Optics, coronagraphs, exoplanets, high contrast, computational methods
\end{keywords}
\maketitle

@@

Initially developed to image the Sun's corona without the need for a Solar eclipse \citep{Lyot33}, one of the most significant science drivers for the latest coronagraphs is in the detection and characterisation of circumstellar material and planets around nearby stars.
%
Young self-luminous gas giant exoplanets have been directly imaged at infrared wavelengths around young stars \citep[see ][ for a review of these detections]{Zurlo24} both in the nearby Galactic field and further away in young stellar OB associations (out to 400 pc), typically these exoplanets have luminosities of $10^{-4}-10^{-6}$ of their parent star at angular separations up to a few arcseconds.

@@

  The upper right part of the figure shows known self-luminous gas giant planets \citep{Lacy20}.

@@

  The lines show  $5\sigma$ point source contrast limits from recent instruments and surveys.

@@

  Figure plot and data from \citet{Bailey24}.

>>>>

\newcommand{\project}[1]{\textsf{#1}}
\hypersetup{%
        colorlinks,
        breaklinks=true,
        plainpages=false,%
        citecolor=[rgb]{0,0.20,0.45},
        linkcolor=[rgb]{0,0.20,0.45},
        urlcolor=[rgb]{0,0.20,0.45},
        bookmarksopen=true,%
        bookmarksnumbered=false,%
        bookmarksdepth=5%
}

\begin{document}

\markboth{Kenworthy \& Haffert}{HCC}

% Title on one line with LARGE
\title{\huge {\normalfont High-Contrast Coronagraphy}}

% large and normalfont to get both names on one line
\author{\large {\normalfont Matthew A. Kenworthy$^1$ and Sebastiaan Y. Haffert$^{1,2}$}
  \affil{$^1$Leiden Observatory, Niels Bohrweg 2, Leiden 2300RA, The Netherlands; email: kenworthy@strw.leidenuniv.nl}
  \affil{$^2$University of Arizona, Steward Observatory, 933 N. Cherry Avenue, Tucson, Arizona, United States; email: haffert@strw.leidenuniv.nl}}

\begin{abstract}
Imaging terrestrial exoplanets around nearby stars is a formidable technical challenge, requiring the development of coronagraphs to suppress the stellar halo of diffracted light at the location of the planet.
%
In this review, we derive the science requirement for high-contrast imaging, present an overview of diffraction theory and the Lyot coronagraph, and define the parameters used in our optimization.
%
We detail the working principles of coronagraphs both in the laboratory and on-sky with current high-contrast instruments, and we describe the required algorithms and processes necessary for terrestrial planet imaging with the extremely large telescopes and proposed space telescope missions:

\begin{itemize}
    \item Imaging terrestrial planets around nearby stars is possible with \\ 
    a combination of coronagraphs and active wavefront control \\
    using feedback from wavefront sensors.
    \item Ground based 8-40m class telescopes can target the habitable \\ 
    zone around nearby M dwarf stars with contrasts of $10^{-7}$ and \\
    space telescopes can search around solar-type stars with \\
    contrasts of $10^{-10}$.
    \item Focal plane wavefront sensing, hybrid coronagraph designs and \\
    multiple closed loops providing active correction are required \\
    to reach the highest sensitivities.
    \item Polarization effects need to be mitigated for reaching $10^{-10}$ \\ contrasts whilst keeping exoplanet yields as high as possible.
    \item Recent technological developments, including photonics and micro-\\
    wave kinetic inductance detectors,
    will be folded into high-contrast \\ instruments.
\end{itemize}

@@

%Keywords, etc.
\begin{keywords}
 optics, coronagraphs, exoplanets, high contrast, computational methods
\end{keywords}
\maketitle

@@

Initially developed to image the Sun's corona without the need for a Solar eclipse \citep{Lyot33}, one of the most significant science drivers for the latest coronagraphs involves the detection and characterisation of circumstellar material and planets around nearby stars.
%
Young self-luminous gas giant exoplanets have been directly imaged at infrared wavelengths around young stars \citep[see ][ for a review of these detections]{Zurlo24} both in the nearby Galactic field and further away in young stellar OB associations (out to 400 pc), typically these exoplanets have luminosities of $10^{-4}-10^{-6}$ of their parent star at angular separations up to a few arcseconds.

@@

  Known self-luminous gas giant planets are shown in the top right \citep{Lacy20}.

@@

  The lines represent $5\sigma$ point source contrast limits from recent instruments and surveys.

@@

  Figure plot and data from \citet{Bailey24} along with references for the contrast curves.
